Methods paper for erosion

### 2017-10-16 docs/methods/erosion_methods.tex
worked on numerics section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature} 
Integrals that need to be approximated are the double-layer potential
for target points both off the boundary~\eqref{eqn:velocityDLP} and on
the boundary~\eqref{eqn:DLP}, the shear
stress~\eqref{eqn:shearStressDLP}, the
vorticity~\eqref{eqn:vorticityDLP}, the pressure both off and on the
boundary~\eqref{eqn:pressureDLP}, the drag~\eqref{eqn:drag}, and the
resistivity.   The shear stress, pressure, and drag must also be
computed using quadrature, and this can be interpreted as a
post-processing step once the density function, Stokeslets, and rotlets
are computed.

The integrands of each of these integrals, except for the resistivity,
are smooth and periodic.  Therefore, the trapezoid rule guarantees
spectral accuracy~\cite{tre-wei2014}.  However, before the trapezoid
rule can be applied, singularity subtraction and odd-even
integration~\cite{sid-isr1988} method must be used.  In addition, when
the target point is near $\bd\Omega$, a near-singular integration scheme
must be used.

\subsubsection{Velocity}
To numerically evaluate the completed double-layer
potential~\eqref{eqn:completed_BIE}, we define $N = MN_\iin + N_\out$ to
be the total number of discretization points of $\bd\Omega$.  The
double-layer potential in~\eqref{eqn:DLP} is discretized with the
trapezoid rule as
\begin{align}
  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
      \Delta s_{j}, \quad i=1,\ldots,N,
  \label{eqn:trapDLP}
\end{align}
where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
$\xx_j$, and
\begin{align*}
  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2},
\end{align*}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the
double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is
replaced with the limiting value of the double-layer potential
\begin{align*}
  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)),
\end{align*}
where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
vector at $\xx \in \bd\Omega$.  The equations for the strengths of the
Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are
also discretized with the trapezoid rule.  Applying this discretization
strategy to~\eqref{eqn:completed_BIE}, the dense linear system that
needs to be solved is
\begin{equation}
  \label{eqn:completed_BIE_discretized}
  \begin{aligned}
    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} +
      \sum_{k=1}^M S[\llambda_k,\cc_k](\xx_i) +
      \sum_{k=1}^M R[\xi_k,\cc_k](\xx_i) + 
      \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
      \nn(\xx_j))\eeta(\xx_j), \\
    \llambda_k &= \sum_{\xx_i \in \gamma_k} \eeta(\xx_i) 
      \Delta s_i \\ 
    \mu_k &= \sum_{\xx_i \in \gamma_k}
      {(\xx_i^k - \cc_k)}^\perp \cdot \eeta(\xx_i^k) \Delta s_i^k,
  \end{aligned}
\end{equation}
for $i=1,\ldots,N$, $k=1,\ldots,M$.

The dense linear system~\eqref{eqn:completed_BIE_discretized} is solved
iteratively with GMRES.  The most expensive part is computing the $N$
term sum for all target points.  A direct summation would require
$\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$ by using the
Fast Mutlipole method for the Stokes double-layer
potential~\cite{gre-rok1987,rac-???} \todo[inline]{sent email to Manas
asking about this}.  Since we are discretizing a second-kind integral
equation, the number of GMRES iterations is bounded independent of
$N$~\cite{cam-ips-kel-mey-xue1996}, and the overall complexity for
solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.

\subsubsection{Shear Stress}
We have decomposed the deformation tensor into the contributions due to
three different terms.  The contributions from the Stokeslets and the
rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
\gamma$.  However, the kernel of the deformation tensor due to the
double-layer potential~\eqref{eqn:shearStressDLP} 
\begin{align*}
  K_\ssigma(\xx,\yy) = \frac{1}{2\pi} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) +
    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
  \right),
\end{align*}
has a singularity that is asymptotic to $\bigO(\rho^2)$ when $\yy
\rightarrow \xx$.  The strength of this singularity can be reduced  by
using the fact that a velocity field due to a constant density function
is constant~\cite{poz1992}.  Therefore, the first part of the
deformation tensor can be evaluated as 
\begin{align*}
  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
\end{align*}
This expression for the deformation tensor has a singularity that is
asymptotic to $\bigO(\rho)$ when $\yy \rightarrow \xx$.  Finally, to
achieve a spectrally accurate discretization for the deformation tensor,
we use odd-even integration~\cite{sid-isr1988}.  That is, the
deformation tensor due to the double-layer potential at a discretization
point $\xx_i$ on body $\gamma_k$, with $i$ being odd, is approximated as
\begin{align*}
  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_k}
    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
  \sum_{\substack{\xx_j \in \gamma_k \\ j \: \mathtt{even}}}
    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
\end{align*}
and a similar approximation is used when $i$ is even.  The deformation
tensor due to the Stokeslets and rotlets is given in
equation~\eqref{eqn:shearStressSR}, and then the shear stress can be
computed by computing the deformation tensor in the normal direction,
and taking the inner product with the tangent direction.

@@

\subsubsection{Vorticity}
Since the vorticity is equivalent to the shear stress on $\bd\Omega$, we
only need to compute the vorticity at target points $\xx \in \Omega$ in
the interior.  This is done with the trapezoid rule by computing
\begin{align*}
  \omega(\xx_i) = \sum_{j=1}^N K_\omega (\xx_i,\xx_j) \cdot \eeta_j 
    \Delta s_j,
\end{align*}
where
\begin{align*}
  K_\omega (\xx,\yy) =  -\frac{\rr}{\pi}
    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}.
\end{align*}

\subsubsection{Pressure}
For the pressure, the double-layer potential is equivalent to
\begin{align*}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
\end{align*}

\subsubsection{Drag}

\subsubsection{Resistivity}

@@

We now introduce the tangent angle, $\theta$, defined through the relation
\begin{equation}
(x_s, y_s) = (\cos \theta, \sin \theta)
\end{equation}
where $s$ is arc length. We also introduce the normalized arc length $\alpha = s / L$. In terms of these new variables, the curvature can be expressed as
\begin{equation}
\kappa = \frac{1}{L} \pderiv{\theta}{\alpha}
\end{equation}
Substitution into Eq.~(\ref{eqn:Vn}) gives
\begin{equation}
\label{eqn:Vn2}
\Vn = \atau + \frac{\eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 2 \pi \right)
\end{equation}
The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced. The tangential velocity that does the trick is determined by \cite{hou-low-she1994}
\begin{equation}
\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
\end{equation}
The interface evolution is then given by
\begin{equation}
\dot{\xx}(t) = \Vn \nn + \Vs \ss.
\end{equation}
Upon transforming to the variables $\theta(\alpha,t)$ and $L(t)$, we obtain the evolution equations
\begin{align}
& \tderiv{L}{t} = - \mean{\thalpha \Vn} \\
& \pderiv{\theta}{t} = \frac{1}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
\end{align}
Inserting Eq.~(\ref{eqn:Vn2}) for the normal velocity gives
\begin{equation}
\pderiv{\theta}{t} = \frac{\eps}{L^{2} \log \left(2\pi/L \right)} \ppd{\theta}{\alpha} 
+ \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
\end{equation}
For simplicity, we introduce the variables
\begin{align}
& M = - \mean{\thalpha \Vn} \\
& N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
& \elfun = \frac{1}{L^{2} \log \left(2\pi/L \right)}
\end{align}
Then the evolution equations can be expressed as
\begin{align}
& \tderiv{L}{t} = M \\
& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
\end{align}
We treat $\theta$ spectrally
\begin{equation}
\theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha}
\end{equation}
Then we get
\begin{equation}
\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun \thhat_k = \hat{N}_k
\end{equation}
We introduce the integrating factor
\begin{equation}
\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun dt \right)
\end{equation}
so that the solution can be represented as
\begin{align}
\thhat_k(t) & = \frac{1}{\mu} \int^t \mu \hat{N}_k dt'
= \thhat_k(0) + \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun dt'' \right) \hat{N}_k \, dt'
% LONGER FORM
%& = \exp \left( -4 \eps \pi^2 k^2 \int_0^t \elfun(L) ds \right) \, 
%\int_0^t \exp \left( 4 \eps \pi^2 k^2 \int_0^s \elfun(L) ds' \right) \hat{N}_k ds \\
\end{align}
where $t'$ and $t''$ are simply dummy variables for integration. We can get the exact relationship
\begin{equation}
\thhat_k(t + \Delta t) = \thhat_k(t) 
+ \int_t^{t+\Delta t} \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^{t+\Delta t} \elfun dt'' \right) \hat{N}_k \, dt'
\end{equation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature} 
Integrals that need to be approximated are the double-layer potential
for for the velocity at target points both off the
boundary~\eqref{eqn:velocityDLP} and on the boundary~\eqref{eqn:DLP},
the shear stress~\eqref{eqn:shearStressDLP}, the
vorticity~\eqref{eqn:vorticityDLP}, the pressure both off and on the
boundary~\eqref{eqn:pressureDLP}, the drag~\eqref{eqn:drag}, and the
resistivity.   The shear stress, pressure, and drag must also be
computed using quadrature, and this can be interpreted as a
post-processing step once the density function, Stokeslets, and rotlets
are computed.

All the integrands, except for the resistivity, are periodic, so the
trapezoid rule guarantees spectral accuracy~\cite{tre-wei2014}.
However, before the trapezoid rule can be applied, singularity
subtraction and odd-even integration~\cite{sid-isr1988} must be used.
In addition, when the target point is near $\bd\Omega$, a near-singular
integration scheme must be used.

\todo[inline]{Organize as first doing points on the boundary (velocity,
shear stress, pressure, drag) and the points off the boundary (velocity,
vorticity, pressure, resistivity)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Velocity}
To numerically evaluate the completed double-layer
potential~\eqref{eqn:completed_BIE}, we define $N = MN_\iin + N_\out$ to
be the total number of discretization points of $\bd\Omega$.  The
double-layer potential in~\eqref{eqn:DLP} is discretized with the
trapezoid rule as
\begin{align}
  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
      \Delta s_{j}, \quad i=1,\ldots,N,
  \label{eqn:trapDLP}
\end{align}
where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
$\xx_j$, and
\begin{align*}
  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2},
\end{align*}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the
double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is
replaced with the limiting value of the double-layer potential
\begin{align*}
  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)),
\end{align*}
where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
vector at $\xx \in \bd\Omega$.  The strengths of the
Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are
also discretized with the trapezoid rule.  Applying this discretization
strategy to~\eqref{eqn:completed_BIE}, the dense linear system that
needs to be solved is
\begin{equation}
  \label{eqn:completed_BIE_discretized}
  \begin{aligned}
    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} +
      \sum_{k=1}^M S[\llambda_k,\cc_k](\xx_i) +
      \sum_{k=1}^M R[\xi_k,\cc_k](\xx_i) + 
      \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
      \nn(\xx_j))\eeta(\xx_j), \\
    \llambda_k &= \sum_{\xx_i \in \gamma_k} \eeta(\xx_i) 
      \Delta s_i \\ 
    \mu_k &= \sum_{\xx_i \in \gamma_k}
      {(\xx_i^k - \cc_k)}^\perp \cdot \eeta(\xx_i^k) \Delta s_i^k,
  \end{aligned}
\end{equation}
for $i=1,\ldots,N$, $k=1,\ldots,M$.  Since all the integrands are smooth
and periodic, by using the trapezoid rule, we are guaranteed that the
numerical solutions converges to the true solution with spectral
accuracy.

The dense linear system~\eqref{eqn:completed_BIE_discretized} is solved
iteratively with GMRES~\cite{saa-sch1986}.  The most expensive part is
computing the $N$ term sum for all target points.  A direct summation
would require $\bigO(N^2)$ operations, but this is reduced to $\bigO(N)$
by using the Fast Mutlipole method for the Stokes double-layer
potential~\cite{gre-rok1987,rac-???} \todo[inline]{sent email to Manas
asking about this}.  Since we are discretizing a second-kind integral
equation, the number of GMRES iterations is bounded independent of
$N$~\cite{cam-ips-kel-mey-xue1996}, and the overall complexity for
solving~\eqref{eqn:completed_BIE_discretized} is $\bigO(N)$.

To compute the velocity at an interior point $\xx \in \Omega$, the
integrand is periodic and smooth, so the trapezoid rule rule achieves
spectral accuracy.  Therefore, the velocity at a target points $\xx \in
\Omega$ is approximate by
\begin{align*}
  \uu(\xx) = \sum_{j=1}^N K(\xx,\xx_j) \eeta(\xx_j) \Delta s_j.
\end{align*}
If the velocity needs to be computed at $N_\tar$ points in $\Omega$,
where $N_\tar$ is large, the FMM is used to reduce the complexity from
$\bigO(N_\tar N)$ to $\bigO(N_\tar + N)$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Stress}
We have decomposed the deformation tensor into the contributions due to
three different terms.  The contributions from the Stokeslets and the
rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
\gamma$.  However, the kernel of the deformation tensor due to the
double-layer potential~\eqref{eqn:shearStressDLP} 
\begin{align*}
  K_\ssigma(\xx,\yy) = \frac{1}{2\pi} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) +
    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
  \right),
\end{align*}
has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
\rightarrow \xx$.  The singularity strength can be reduced since the
velocity corresponding to a constant density function is
constant~\cite{poz1992}.  Therefore, the deformation tensor of the
double-layer potential is equivalent to
\begin{align*}
  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
\end{align*}
This expression for the deformation tensor has a singularity that is
asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
to achieve spectral accuracy, we apply odd-even
integration~\cite{sid-isr1988}.  That is, the deformation tensor due to
the double-layer potential at a discretization point $\xx_i$ on body
$\gamma_k$, with $i$ being odd, is approximated as
\begin{align*}
  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_k}
    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
  \sum_{\substack{\xx_j \in \gamma_k \\ j \: \mathtt{even}}}
    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
\end{align*}
and a similar approximation is used when $i$ is even.  The deformation
tensor due to the Stokeslets and rotlets is given in
equation~\eqref{eqn:shearStressSR}, and then the shear stress can be
computed by computing the deformation tensor in the normal direction,
and taking the inner product with the tangent direction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vorticity}
Since the vorticity is equivalent to the shear stress on $\bd\Omega$, we
only need to compute the vorticity at target points at interior points
$\xx \in \Omega$.  This is done with the trapezoid rule by computing
\begin{align*}
  \omega(\xx_i) = \sum_{j=1}^N K_\omega (\xx_i,\xx_j) \cdot \eeta_j 
    \Delta s_j,
\end{align*}
where
\begin{align*}
  K_\omega (\xx,\yy) =  -\frac{\rr}{\pi}
    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}.
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Pressure}
For the pressure, the double-layer potential is equivalent to
\begin{align*}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Drag}

@@

We now introduce the tangent angle, $\theta$, defined through the relation
\begin{equation}
\left( \pderiv{x}{s}, \pderiv{y}{s} \right) = \left(\cos \theta, \sin \theta \right)
\end{equation}
where $s$ is arc length. We also introduce the normalized arc length $\alpha = s / L$. In terms of these new variables, the curvature can be expressed as
\begin{equation}
\kappa = \frac{1}{L} \pderiv{\theta}{\alpha}
\end{equation}
Substitution into Eq.~(\ref{eqn:Vn}) gives
\begin{equation}
\label{eqn:Vn2}
\Vn = \atau + \frac{\eps}{L \log \left(2\pi/L \right)}  \left(\pderiv{\theta}{\alpha} - 2 \pi \right)
\end{equation}
The main idea is to introduce an artificial tangential velocity that keeps collocation points equally spaced with respect to arc length; i.e.~the grid of $\alpha$ should always remain equally spaced. The tangential velocity that does the trick is determined by \cite{hou-low-she1994}
\begin{equation}
\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn}
\end{equation}
The interface evolution is then given by
\begin{equation}
\dot{\xx}(t) = \Vn \nn + \Vs \ss.
\end{equation}
Upon transforming to the variables $\theta(\alpha,t)$ and $L(t)$, we obtain the evolution equations
\begin{align}
& \tderiv{L}{t} = - \mean{\thalpha \Vn} \\
& \pderiv{\theta}{t} = \frac{1}{L} \left( \pderiv{\Vn}{\alpha} + \thalpha \Vs \right)
\end{align}
Inserting Eq.~(\ref{eqn:Vn2}) for the normal velocity gives
\begin{equation}
\pderiv{\theta}{t} = \frac{\eps}{L^{2} \log \left(2\pi/L \right)} \ppd{\theta}{\alpha} 
+ \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right)
\end{equation}
For simplicity, we introduce the variables
\begin{align}
& M = - \mean{\thalpha \Vn} \\
& N = \frac{1}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
& \elfun = \frac{1}{L^{2} \log \left(2\pi/L \right)}
\end{align}
Then the evolution equations can be expressed as
\begin{align}
& \tderiv{L}{t} = M \\
& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + N
\end{align}
We treat $\theta$ spectrally
\begin{equation}
\theta(\alpha,t) = \sum_{k = -\infty}^{\infty} \thhat_k e^{2\pi i k \alpha}
\end{equation}
Then we get
\begin{equation}
\tderiv{\thhat_k}{t} +  4 \eps \pi^2 k^2  \elfun \thhat_k = \hat{N}_k
\end{equation}
We introduce the integrating factor
\begin{equation}
\mu = \exp \left( 4 \eps \pi^2 k^2 \int \elfun dt \right)
\end{equation}
so that the solution can be represented as
\begin{align}
\thhat_k(t) & = \frac{1}{\mu} \int^t \mu \hat{N}_k dt'
= \thhat_k(0) + \int_0^t \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^t \elfun dt'' \right) \hat{N}_k \, dt'
% LONGER FORM
%& = \exp \left( -4 \eps \pi^2 k^2 \int_0^t \elfun(L) ds \right) \, 
%\int_0^t \exp \left( 4 \eps \pi^2 k^2 \int_0^s \elfun(L) ds' \right) \hat{N}_k ds \\
\end{align}
where $t'$ and $t''$ are simply dummy variables for integration. We can get the exact relationship
\begin{equation}
\thhat_k(t + \Delta t) = \thhat_k(t) 
+ \int_t^{t+\Delta t} \exp \left( -4 \eps \pi^2 k^2 \int_{t'}^{t+\Delta t} \elfun dt'' \right) \hat{N}_k \, dt'
\end{equation}
